### 2018-06-21 latex/figurelegends.tex
Indicated enzymes in figure by colour instead of number as before. Adjusted text accordingly.

Deuterostomia that encode NNMT show a sequence insertion in the N-terminal region of NamPRT. A) Multiple sequence alignment of NamPRT of selected deuterostomes show a sequence insertion in organisms that encode NamPRT and NNMT. (Species names are given and the number in parenthesis indicates the enzyme combination encoded in these species; 3 – NADA and NamPRT, 6 – NamPRT and NNMT, 7 – NADA, NamPRT and NNMT. \todo[author=Mathias]{Note to myself: replace the numbers by something better and rewrite this part.}) The nuclear localisation signal (NLS\todo[author=Mathias]{Note to myself: Write “predicted NLS” in figure}) indicated, was predicted using using cNLS-mapper (\url{http://nls-mapper.iab.keio.ac.jp/cgi-bin/NLS_Mapper_form.cgi} \cite{Kosugi2009}).

@@

C) The localisation of wildtype NamPRT varies between pure cytosolic and mixed cytosolic-nuclear localisation. This is not changed in the mutant missing the insert that corresponds to the unresolved loop structure.

>>>>

Deuterostomia that encode NNMT show a sequence insertion in the N-terminal region of NamPRT. A) Multiple sequence alignment of NamPRT of selected deuterostomes show a sequence insertion in organisms that encode NamPRT and NNMT. Coloured circles indicate the enzymes present in the species; blue: NamPRT and NNMT; black: NamPRT, NADA, and NNMT; yellow: NamPRT and NADA.

@@

### 2018-06-21 latex/results.tex
Indicated enzymes in figure by colour instead of number as before. Adjusted text accordingly.

As our simulations suggest that NNMT might have excerted an evolitionary pressure on the development of NamPRT. We performed multiple sequence analysis to see if we can find sequence variations in the protein sequence of NamPRT that indicate evolutionary changes of NamPRT upon the appearance of NNMT. The multiple sequence alignment of selected sequences is shown in Figure 5A and Supplementary Figure ?\todo[author=Mathias B.]{Full MSA to be prepared as suppl figure.} We recognized that Deuterostomia that have only NamPRT and NNMT (indicated by the number 6 in parenthesis \todo[author=Mathias B.]{Maybe rather indicate this by colour and the kingdom through abbrev?}) have an insert of ten amino acids corresponding to positions 43 to 52 of the human enzyme, that overlaps with a predicted weak nuclear localisation signal, that is lost when removing this sequence stretch. 
Furthermore, the inserted sequence corresponce to an structurallly unresolved loop structure in all avaibable crystal structure of human NamPR (e.g. \cite{Wang2006} structure visualisation Figure 5B). The loop is connected to one of the beta-sheets involved in substrate binding.

>>>>

As our simulations suggest that NNMT might have excerted an evolitionary pressure on the development of NamPRT. We performed multiple sequence analysis to see if we can find sequence variations in the protein sequence of NamPRT that indicate evolutionary changes of NamPRT upon the appearance of NNMT. The multiple sequence alignment of selected sequences is shown in Figure 5A and Supplementary Figure ?\todo[author=Mathias B.]{Full MSA to be prepared as suppl figure.} We recognized that Deuterostomia that have only NamPRT and NNMT (indicated by the blue circle) have an insert of ten amino acids corresponding to positions 43 to 52 of the human enzyme, that overlaps with a predicted weak nuclear localisation signal, that is lost when removing this sequence stretch.
Furthermore, the inserted sequence corresponce to an structurallly unresolved loop structure in all avaibable crystal structure of human NamPR (e.g. \cite{Wang2006} structure visualisation Figure 5B). The loop is connected to one of the beta-sheets involved in substrate binding.
